---
title: "Project Drawdown Solutions help to meet many Sustainable Development Goals"
output: 
  html_document: 
    fig_height: 7
    fig_width: 10
    keep_md: yes
    self_contained: no
---

*By [Amy Quinton][7] and [Daniel Newman][8]*


All [United Nations (UN) countries][4] are working towards achieving the [Sustainable Development Goals (SDGs)][1] by 2030. [169 targets][5] and [232 unique indicators][6] measure progress on the [17 SDGs][1].
```{r, SDG_image_url, echo=FALSE}
# Define variable containing SDG image url
SDG_image_url <- "http://www.un.org/development/desa/disabilities/wp-content/uploads/sites/15/2015/10/SDG-Poster.png"
```
[![](`r SDG_image_url`)][1]

[Climate Action][9] is one of these [17 SDGs][1] that the world has agreed is of critical importance, and it is underpinned by the [Paris Agreement][17]. A separate initiative, [Project Drawdown][2], has identified a range of solutions to limit climate change ("Drawdown Solutions"), ranked via objective measures of CO2-equivalent reduction and costs. 

*We realised that most [Drawdown Solutions][3] provide extra sustainable development benefits, additional to climate action, which relate directly to many of the [17 SDGs][1].* So we attempted to categorise which of [Project Drawdown's top 76  solutions][3] related to which of the [17 SDGs][1].

This is timely as the [UN Department of Economic and Social Affairs][15] (UN DESA) and the [UN Framework Convention on Climate Change][16] (UNFCCC) have just published new analysis titled ["Maximizing Co-benefits by Linking Implementation of the Sustainable Development Goals and Climate Action"][14].

The figure and table below shows our rudimentary assessment that the [Project Drawdown's solutions][3] make a positive contribution to 16 of the [17 SDGs][1], not just to the Climate Action SDG! 



```{r load-libraries-and-download-sheet, echo=FALSE, include=FALSE}
#install.packages(c("googlesheets4", "tidyverse","treemapify","knitr", "kableExtra", "googledrive"))
#install.packages("devtools")
#devtools::install_github("tidyverse/googlesheets4")
library(googlesheets4)
library(tidyverse)
library(treemapify)
library(knitr)
library(kableExtra)
library(googledrive) 

drive_auth(email = TRUE)

# google sheets URL"
sheet_url <- "https://docs.google.com/spreadsheets/d/1hq5frci8R4o5kor4oraealN66X1av1IhkZmOydjORrQ/edit?usp=sharing"

# download google sheet:
drawdown_sdg <- read_sheet(ss = sheet_url, sheet = 1)
```

```{r reshape-data, echo=FALSE, include=FALSE}
# rename some variables:
drawdown_sdg %>%
  rename(rank = Rank,
         solution = Solution,
         sector = Sector) -> drawdown_sdg

# reshape drawdown_sdg data into "long" format:
drawdown_sdg %>%
  select(solution, SDG1, SDG2, SDG3, SDG4, SDG5, SDG6) %>%
  pivot_longer(c(-solution), names_to = "sdg_number", values_to = "sdg", values_drop_na = T) %>%
  select(solution, sdg) -> long

# Join TOTAL_ATMOSPHERIC_CO2_EQ_REDUCTION_GT to "long" dataframe:
drawdown_sdg %>%
  select(solution, TOTAL_ATMOSPHERIC_CO2_EQ_REDUCTION_GT) -> to_join
long %>%
  full_join(to_join) -> long
rm(to_join)

# check to make sure SDGs haven't been assigned twice to the same drawdown solution:
long %>%
  group_by(solution, sdg) %>%
  summarise(n = n()) %>%
  ungroup() %>%
  summarise(max = max(n)) #should be max 1
```

```{r, echo=FALSE, include=FALSE}
# Which Drawdown Solutions cover the most SDGs? see "num_sdgs_per_drawdown" dataframe created below:
long %>%
  group_by(solution) %>%
  summarise(num_sdgs = n_distinct(sdg)) %>%
  arrange(desc(num_sdgs)) -> num_sdgs_per_drawdown

# Which SDGs have the most Drawdown Solutions? see "num_drawdowns_per_sdg" dataframe created below:
long %>%
  group_by(sdg) %>%
  summarise(num_drawdowns = n_distinct(solution),
            total_co2_eq = sum(TOTAL_ATMOSPHERIC_CO2_EQ_REDUCTION_GT)) %>%
  arrange(desc(num_drawdowns)) -> num_drawdowns_per_sdg

# create a dataframe called "select_order" below that gets the column names in the order we will need 
# so that SDGs with more related Drawdown Solutions appear in columns towards the left:
num_drawdowns_per_sdg %>%
  mutate(sdg = chartr(x = sdg, old = "_", new = " ")) %>%
  arrange(desc(num_drawdowns)) %>%
  select(sdg) %>%
  mutate(values_from = NA) %>%
   pivot_wider(names_from = sdg, values_from = values_from) %>%
  names() -> select_order
```


## Project Drawdown's solutions address many of the SDGs
**The size of each rectangles corresponds to the number of Drawdown Solutions that could help achieve the SDG. So the bigger the SDG rectangle, the more Drawdown Solutions could be applied.**
```{r treemap1,  echo=FALSE}
# create the treemap plot:
num_drawdowns_per_sdg %>%
  mutate(sdg = chartr(x = sdg, old = "_", new = " ")) %>%
  mutate(sdg = paste("SDG", sdg, sep = " ")) %>%
  ggplot(aes(area = num_drawdowns, label= sdg, fill = num_drawdowns))  +
  geom_treemap() +
  geom_treemap_text(fontface = "italic", colour = "white", place = "centre",
                    grow = F, min.size = 1, reflow = T) +
  theme(legend.position="none") 
```

### The data pertaining to the plot above 
**SDGs with more related Drawdown Solutions appear in columns towards the left:**<br>
<sub>*Scroll over the table to navigate*

```{r table1, echo=FALSE}
# set defult options for knitr to use when it creates the tables below:
options(knitr.kable.NA = '',
        knitr.table.format = 'markdown') 

long %>%
  mutate(sdg = chartr(x = sdg, old = "_", new = " ")) %>%
  select(sdg, solution) %>%
   group_by(sdg) %>%
   mutate(rn = row_number()) %>% # recreated unique identifier column
  pivot_wider(names_from = sdg, values_from = solution) %>%
  select(select_order) -> for_table

# make first table 
kable(for_table, "html") %>%
  kable_styling("striped") %>% 
  scroll_box(height = "1200px", width = "900px")

```

### From the other perspective, which of the Drawdown Solutions relates to the most SDGs? 

The table below shows our assessment that the [Educating Girls][10] and [Reduced Food Waste][11] Drawdown Solutions are related to the most SDGs, each applicable to (at least) 6 SDGs:

- *Educating Girls:* 
  - Climate Action; Gender Equality; No Poverty;	Decent Work and Economic Growth; Reduced Inequality; Quality Education.

- *Reduced Food Waste:* 
  - Climate Action;	Zero Hunger; Good Health and Well being;	Sustainable Cities and Communities; Responsible Consumption and Production; Life on Land.
  
The table below shows our rudimentary assessment of the number of related SDGs for each of the 76 best Drawdown Solutions  

**Number of related SDGs for each of the 76 best Drawdown Solutions:**<br>
<sub>*Scroll over the table to navigate*

```{r table2, echo=FALSE}
# make 2nd table
num_sdgs_per_drawdown %>%
  rename(`Drawdown Solution` = solution,
         `Number of related SDGs` = num_sdgs) %>%
  kable("html") %>% 
  kable_styling("striped") %>% 
  scroll_box(height = "300px")
```

## Open data and code from this analysis
We hope this post is interesting and thought provoking. If anybody would like to contribute further to it, [here][12] is the spreadsheet containing our rough analysis. Anyone can add comments/suggestions. We will recieve an email notification when people comment. Also [here][13] is a repository with the code we used to produce everything else in this post (pull requests welcome). 

## Conclusions
Our rudimentary analysis shows that the [Drawdown Solutions][3] provide well described and measurable ways to address climate change while also contributing to a broad range of other SDGs and benefits. 

This aligns with UN DESA and UNFCCC's [lastest report][14] on the synergies between global commitments to climate action and the SDGs.

We hope this is useful for governments, businesses, not-for-profits and others looking for direct ways to contribute towards the [Sustainable Development Goals (SDGs)][1].


[1]: https://sustainabledevelopment.un.org/sdgs
[2]: https://www.drawdown.org
[3]: https://www.drawdown.org/solutions
[4]: https://en.wikipedia.org/wiki/Member_states_of_the_United_Nations
[5]: https://unstats.un.org/sdgs/indicators/Global%20Indicator%20Framework%20after%20refinement_Eng.pdf
[6]: https://sustainabledevelopment.un.org/content/documents/11803Official-List-of-Proposed-SDG-Indicators.pdf
[7]: https://amyquinton.github.io/about/
[8]: https://dpnewman.com/
[9]: https://sustainabledevelopment.un.org/sdg13
[10]: https://www.drawdown.org/solutions/women-and-girls/educating-girls
[11]: https://www.drawdown.org/solutions/food/reduced-food-waste
[12]: https://docs.google.com/spreadsheets/d/1hq5frci8R4o5kor4oraealN66X1av1IhkZmOydjORrQ/edit?usp=sharing
[13]: https://github.com/amyquinton/drawdown-sdg/blob/master/drawdown-sdgs.Rmd
[14]: https://sustainabledevelopment.un.org/?page=view&nr=1632&type=230&menu=2059
[15]: https://www.un.org/development/desa/en/
[16]: https://unfccc.int/
[17]: https://unfccc.int/process-and-meetings/the-paris-agreement/the-paris-agreement